### 2023-11-26 paper.tex
Worked on interoperability todos

Health Analytics Data-to-Evidence Suite (HADES) is a collection of 20 R packages, developed by the OHDSI team, that interact directly with the OMOP CDM to support large-scale analytics, including cohort construction (CirceR, CohortGenerator), population-level estimation (CohortMethod), patient-level prediction (PatientLevelPrediction), and return statistics, figures, and tables.

@@

TODO: Add database connector example
TODO: Reference database connector example
TODO: Reference that it was inspired by database connector OHDSI package
TODO: Mention package extensions utility

@@

TODO: Discuss OHDSIAPI.jl

>>>>

@@

DBConnector.jl was inspired by the package \textit{DatabaseConnector} (Link: https://github.com/OHDSI/DatabaseConnector)

TODO: Add database connector example
TODO: Reference database connector example
TODO: Mention package extensions utility

@@

In order to more effectively bridge the JuliaHealth ecosystem with ongoing efforts in other ecosystems, Julia provides methods to allow one to seamlessly interoperate with not only other ecosystems but entirely different languages as well.
For example, through the work of packages like RCall.jl or PythonCall.jl, one can utilize R or Python packages and interfaces directly within Julia. \cite{PythonCall.jl} \cite{RCallJl}
This embedding allows one to patch one's workflow where proper tools are missing with the equivalent package in Python or R.

One particular ecosystem is the OHDSI Health Analytics Data-to-Evidence Suite (HADES) ecosystem where the majority of its tools are written in a combination of R and Java.
HADES is a collection of approximately 20 packages, developed by the OHDSI community to interact directly with the OMOP CDM to support large-scale analytics.
The goals of HADES is much the same as the JuliaHealth observational health subecosystem such as supporting cohort construction, population-level estimation, patient-level prediction, and calculating other sorts of relevant research artifacts.

For HADES tools that expose APIs, rather than having to somehow wrap around this with a tool like RCall.jl, instead, HADES software can continue to run as a service and OHDSIAPI.jl can be used.
OHDSIAPI.jl is a Julia wrapper around a variety of OHDSI API-based services that can directly interface with such services.
This can be a great bridging mechanism so that observational health researchers can continue doing work and still interact with necessary research endpoints as needed without interrupting their workflow.
